Reply To Examiners

### 2014-04-25 answer_thesis_examiner/chap2.tex
auto

\noindent
\begin{longtable}[c]{p{0.14\textwidth}|p{0.12\textwidth}|p{0.34\textwidth}|p{0.24\textwidth}}
\textbf{Page No} & \textbf{Line No} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
 \endhead
ToC & - & missing page numbers & Rectified \\
 & & & \\
1 & 13 & single SAR channel & single-channel SAR \\ 
 & & & \\
3 & 12 & Similarly speaking, & Similarly, \\
3 & 19 & criteria & criterion \\ 
4 & 14 & MMSE criteria & MMSE criterion \\
6 & 9 & Last but certainly not least, & Thirdly, \\ 
6 & 9 & such a framework allow & such a framework allows \\[10pt]
ToC & - & missing page numbers & Rectified \\[10pt]
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
\end{longtable}

%\noindent
%\begin{tabularx}{\textwidth}{X | X | X X X X}
%  Page No & Line No & \multicolumn{2}{l|}{Comment} & \multicolumn{2}{l}{Reply} \\
%  \hline 
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR} \\ 
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR} \\ 
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%          \end{tabularx}

>>>>

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
 \endhead
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
3 & 12 & Similarly speaking, & Similarly, \\
3 & 19 & criteria & criterion \\ 
4 & 14 & MMSE criteria & MMSE criterion \\
6 & 9 & Last but certainly not least, & Thirdly, \\ 
6 & 9 & such a framework allow & such a framework allows \\
9 & 7 & multidimensional & Multi-dimensional \\
10 & 12 & The model os & The model is \\
11 & 28 & chapter 5 & Chapter 5 \\
12 & 6 & chapter 6 & Chapter 6 \\
22 & 15 & RadarSat & RadarSat-2 \\
24 & 14 & SVM & SVM (Support Vector Machine) \\
35 & 6-7 & Rician distribution [48]... & Rician distribution [48]. \\
35 & 11 & back scattering & backscattering \\
36 & 10 & literatured & literatures \\
37 & -2 & Proposed bu & proposed by \\
39 & 4 & dependence & dependency \\
44 & -1 & The nature of SAR is ... heteroskedastic heterogeneously & the sentence is rephrased \\
\end{longtable}
